rang: Reconstructing reproducible R computing environments with ease

### 2023-02-12 paper/paper.rmd
Rewrite the paper to reflect the name change

---
title: 'gran: Reconstructing reproducible R computing environments with ease'
tags:
  - R
  - reproducibility
  - docker
authors:
  - name: "Chung-hong Chan"
    orcid: 0000-0002-6232-7530
    affiliation: GESIS Leibniz-Institut für Sozialwissenschaften
abstract: |
  Enter the text of your abstract here.
keywords:
  - blah
  - blee
  - bloo
  - these are optional and can be removed
date: 02 February 2023
year: 2023
bibliography: paper.bib
biblio-style: unsrt
output: rticles::arxiv_article
---

@@

These solutions are better for prospective usage, i.e. using them now to ensure the reproducibility of the current research for future researchers. `gran` targets mostly on retrospective usage, i.e. using `gran` to reconstruct historical R computational environments which have not been completely declared. One can think of `gran` as an archaeological tool. In the following examples, `gran` is used to enable the reproducibility of published literature.

@@

There are two important functions of `gran`: `resolve()` and `dockerize()`.

@@

```r
library(gran)
graph <- resolve(pkgs = c("openNLP", "LDAvis", "topicmodels", "quanteda"),
                 snapshot_date = "2020-01-16")
graph
```

The resolved result is an S3 object called `granlist`. The information contained in a `granlist` can then be used to construct a computational environment in the similar manner as `containerit`, but with the packages and R versions pinned on the snapshot date. Then, `dockerize()` is used to generate the `Dockerfile` and other scripts in the `output_dir`. For R >= 3.1, the images from the Rocker project are used [@boettiger:2017:IR]. For R < 3.1 but >= 2.1, a custom image based on Debian Woody is used. As of writing, `gran` does not support R < 2.1, i.e. snapshot date earlier than 2005-04-19. The development to support R < 2.1 is in progress.

```r
dockerize(granlist graph, output_dir = "docker")
```

@@

```r
dockerize(granlist graph, output_dir = "docker", cache = TRUE)
```

@@

```r
dockerize(granlist graph, output_dir = "docker", cache = TRUE,
          lib = "anotherlibrary")
```

@@

```bash
cd docker
## might need to sudo
docker build -t gran .
docker run --rm --name "grantest" -ti gran
```

@@

Using `gran`, one can query the version of `quanteda` on 2018-10-06 and create a Docker container with all the "period appropriate" dependencies. Here, the `rstudio` Rocker image is selected.

```r
library(gran)
graph <- resolve(pkgs = "quanteda",
                 snapshot_date = "2018-10-06",
                 os = "ubuntu-18.04")
dockerize(graph, output_dir = "quanteda_docker",
          image = "rstudio")
```

@@

```{r, fig.cap = "The code snippet running in a R 3.5.1 container created with gran", echo = FALSE}
knitr::include_graphics("quanteda_rstudio.png", dpi = 300)
```

>>>>

---
title: 'rang: Reconstructing reproducible R computing environments with ease'
tags:
  - R
  - reproducibility
  - docker
authors:
  - name: "Chung-hong Chan"
    orcid: 0000-0002-6232-7530
    affiliation: GESIS Leibniz-Institut für Sozialwissenschaften
  - name: "David Schoch"
    orcid: 0000-0003-2952-4812
    affiliation: GESIS Leibniz-Institut für Sozialwissenschaften    
abstract: |
  Enter the text of your abstract here.
keywords:
  - blah
  - blee
  - bloo
  - these are optional and can be removed
date: 02 February 2023
year: 2023
bibliography: paper.bib
biblio-style: unsrt
output: rticles::arxiv_article
---

@@

These solutions are better for prospective usage, i.e. using them now to ensure the reproducibility of the current research for future researchers. `rang` targets mostly on retrospective usage, i.e. using `rang` to reconstruct historical R computational environments which have not been completely declared. One can think of `rang` as an archaeological tool. In the following examples, `rang` is used to enable the reproducibility of published literature.

@@

There are two important functions of `rang`: `resolve()` and `dockerize()`.

@@

```r
library(rang)
graph <- resolve(pkgs = c("openNLP", "LDAvis", "topicmodels", "quanteda"),
                 snapshot_date = "2020-01-16")
graph
```

The resolved result is an S3 object called `rang`. The information contained in a `rang` can then be used to construct a computational environment in the similar manner as `containerit`, but with the packages and R versions pinned on the snapshot date. Then, `dockerize()` is used to generate the `Dockerfile` and other scripts in the `output_dir`. For R >= 3.1, the images from the Rocker project are used [@boettiger:2017:IR]. For R < 3.1 but >= 2.1, a custom image based on Debian Woody is used. As of writing, `rang` does not support R < 2.1, i.e. snapshot date earlier than 2005-04-19. The development to support R < 2.1 is in progress.

```r
dockerize(graph, output_dir = "docker")
```

@@

```r
dockerize(graph, output_dir = "docker", cache = TRUE)
```

@@

```r
dockerize(graph, output_dir = "docker", cache = TRUE,
          lib = "anotherlibrary")
```

@@

```bash
cd docker
## might need to sudo
docker build -t rang .
docker run --rm --name "rangtest" -ti rang
```

@@

Using `rang`, one can query the version of `quanteda` on 2018-10-06 and create a Docker container with all the "period appropriate" dependencies. Here, the `rstudio` Rocker image is selected.

```r
library(rang)
graph <- resolve(pkgs = "quanteda",
                 snapshot_date = "2018-10-06",
                 os = "ubuntu-18.04")
dockerize(graph, output_dir = "quanteda_docker",
          image = "rstudio")
```

@@

```{r, fig.cap = "The code snippet running in a R 3.5.1 container created with rang", echo = FALSE}
knitr::include_graphics("quanteda_rstudio.png", dpi = 300)
```
